Secure Composition \\ of Robust and Optimising Compilers \vspace{-1.5em}

### 2024-05-28 csf2/main.tex

The language also adds user annotations $\obj{\securitytag{}}$ for the secrecy of variables, which can be either private (high secrecy) $\obj{\lock}$ or public (low secrecy) $\obj{\unlock}$.
Security tags $\obj{\securitytag{}}$ are arranged in the usual secrecy lattice~\MP{NI cits}, where $\obj{\lock}\sqsubseteq\obj{\securitytag{}}$ and $\obj{\securitytag{}}\sqsubseteq\obj{\unlock}$.

>>>>

The language also adds user annotations $\obj{\securitytag{}}$ for the secrecy of variables, which can be either private (high secrecy) $\obj{\lock}$ or public (low secrecy) $\obj{\unlock}$.
Security tags $\obj{\securitytag{}}$ are arranged in the usual secrecy lattice~\cite{zdancewicphd}, where $\obj{\lock}\sqsubseteq\obj{\securitytag{}}$ and $\obj{\securitytag{}}\sqsubseteq\obj{\unlock}$.
